---
title: "2016 r/changemyview Submissions and their Authors"
resource_files:
- cmv_auth_subs.feather
- cmv_subs.feather
- dat_model.feather
runtime: shiny
output:
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
---
```{r init, include = FALSE, verbose=FALSE, echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(verbose=FALSE, echo=FALSE, warning=FALSE, message=FALSE)
library(flexdashboard)
library(tidyverse)
library(stringr)
library(plotly)
library(shiny)
library(lubridate)
library(feather)
library(DT)
library(ineq)
library(anytime)
library(tidytext)
library(wordcloud)
library(stringr)

theme_set(theme_minimal())

# Read in the main data files
dat_cmv_auth_subs <- read_feather("cmv_auth_subs.feather") %>%
  mutate(date = anytime(created_utc))
                           
dat_cmv_subs <- read_feather("cmv_subs.feather") %>%
  mutate(date = anytime(created_utc),  
         tot_deltas = cumsum(OP_gave_delta))
```

Introduction and Glossary
==============================================================================

Column
--------------------------------------------------------------------------------

### What is r/changemyview?

[r/changemyview](https://reddit.com/r/changemyview) is a subreddit where redditors post their opinions as submissions, and
other redditors respond in an attempt to change their opinion. If the original poster (OP)
changes their opinion, then can award the comment that changed their opinion with a 
"delta" that is added to the comment author's lifetime "deltas" received in the subreddit, if no
deltas are awarded, it's assumed that the opinion of the OP's opinion did not change. 

All of the submissions (opinions) posted in 2016 have been gathered, as well as the
entire submission history of the authors who posted their submissions. Ahead you can
observe the frequency of opinions where the OP gave at least one delta, or no delta,
the individual submissions with statistics from the author's history presented, as well
as trends of individual authors' submission scores and submission frequency.

Column
--------------------------------------------------------------------------------
### Key Terms

#### Sentiment
The sentiment of the content (view/opinion) of a r/changemyview submission as 
measured by VADER (Valence Aware Dictionary and sEntiment Reasoner) using Python's
NLTK Library. `-1` (red) indicates full negative sentiment, `0` (white) full neutural,
and `1` (green) full positive sentiment.

#### Total Comments: 
All of the comments made in the changemyview submission.

#### Direct Replies:
Comments made directly responding to the content of the submission.

#### Author Replies:
Responses from the author of the submission to any comment made in the submission.

#### Prior Submissions:
The number of submissions the author made before the current submission.

#### Score
The net of (thumbs) up votes and down votes a submission has received.

#### Subreddit Inequality:
A measure of how unequal the concentration of subreddits are for the prior
submissions. `100%` (black) indicates every submissions was in the same subreddit, while `0%` (white)
indicates that every submission was in a different subreddit. This is simply the
Gini Index in percentage form.

r/changemyview Submissions Delta Trend {data-orientation=rows}
==============================================================================

Filter r/changemyview submissions {.sidebar}
-------------------------------------------------------------------------------
```{r filter_date}
# Posts are only for 2016
start_date <- mdy("1/1/16")
end_date <- mdy("12/31/16")


# Slider Inputs for filtering submissions
sliderInput(
  "cmv_time_range",
  label = "Select Time Span",
  min = start_date,
  max = end_date,
  value = c(start_date, end_date),
  ticks = FALSE,
  timeFormat = "%m/%d"
)

# Binwidth for geom_freqpoly
sliderInput(
  "cmv_bin_width",
  label = "# Days Smoothing",
  min = 1,
  max = 30,
  value = 7
)

# Select the range of lowest setniment to highest sentiment to view.
sliderInput(
  "cmv_sent_range",
  label = "Sentiment",
  min = -1,
  max = 1,
  step = .1,
  value = c(-1, 1)
)

# How many total comments are in a submission.
sliderInput("user_comment_range",
            label = "Total Comments",
            min = 0,
            max = 4903,
            value = c(0, 4903))

# How many direct comments are in a submission.
sliderInput("root_comment_range",
            label = "Direct Replies",
            min = 0,
            max = 224,
            value = c(0, 224))

# How many times the OP commented in their own submission.
sliderInput(
  "OP_com_range",
  label = "Original Poster (OP) Comments",
  min = 0,
  max = 274,
  value = c(0, 274)
)
```

Row
-------------------------------------------------------------------------------

### Submission Frequency 
```{r}
# Dataset filtered from the sliders above.
reac_dat_cmv_sub <- reactive({
  filtered_subs <- dat_cmv_subs %>%
    filter(date >= input$cmv_time_range[1] &
             date <= input$cmv_time_range[2],
           sentiment >= input$cmv_sent_range[1] & 
             sentiment <= input$cmv_sent_range[2],
           num_OP_comments >= input$OP_com_range[1] &
             num_OP_comments <= input$OP_com_range[2],
           num_root_comments >= input$root_comment_range[1] & 
             num_root_comments <= input$root_comment_range[2],
           num_user_comments >= input$user_comment_range[1] & 
             num_user_comments <= input$user_comment_range[2]) %>%
    mutate(OP_gave_delta = ifelse(OP_gave_delta == TRUE,
                                  "Opinion Changed",
                                  "Opinion Stable"))
})

# This plots the filtered data as a timeline with two lines:
# - The Frequency over the bin width of stable and changed opinions
renderPlotly({
    time_series <- plotly_build(
      
      # GGplot object
      ggplot(reac_dat_cmv_sub(), 
           aes(date, color = OP_gave_delta)) +
                            # A day is 86400 in UTC epoch
      geom_freqpoly(binwidth = 86400 * input$cmv_bin_width, pad = FALSE) + 
      scale_color_manual(labels = c("No Change", "Change"),
                         values = c("green", "red")) + 
      # scale_y_continuous(labels = scales::percent) +
      labs(title = "",
           subtitle = "",
           x = "Date",
           y = "# Submissions",
           color = "Opinion changed?"
           )
  )
  
  # Hackish way to make the tooltips better looking and include % that each category consists of the total
  raw_change_text <- time_series$x$data[[1]]$text
  raw_stable_text <- time_series$x$data[[2]]$text
  change_text_split <- matrix(unlist(str_split(raw_change_text,
                                                   "<br />", 3)), ncol = 3, byrow = TRUE) 
  
  total_submissions <- time_series$x$data[[1]]$y + time_series$x$data[[2]]$y
  
  change_text_label <- tibble(count = as.numeric(str_replace(str_extract(change_text_split[, 1], ":(.*)"), ":", "")),
                              date = strftime(anytime(as.numeric(str_replace(str_extract(change_text_split[, 2], ":(.*)"), ":", ""))), format = "%m/%d"),
                              date_beg = strftime(anytime(as.numeric(str_replace(str_extract(change_text_split[, 2], ":(.*)"), ":", "")) - 86400 * input$cmv_bin_width), format = "%m/%d"),
                              status = str_replace(str_extract(change_text_split[, 3], ":(.*)"), ":", ""),
                              percent = 100 * count / total_submissions) %>%
    mutate(label = sprintf("Submissions: %s (%.1f of Total%%)\n%s - %s",  count, percent, date_beg, date)) %>%
    select(label)
  
  stable_text_split <-  matrix(unlist(str_split(raw_stable_text,
                                                   "<br />", 3)), ncol = 3, byrow = TRUE)
  stable_text_label <- tibble(count = as.numeric(str_replace(str_extract(stable_text_split[, 1], ":(.*)"), ":", "")),
                              date = strftime(anytime(as.numeric(str_replace(str_extract(stable_text_split[, 2], ":(.*)"), ":", ""))), format = "%m/%d"),
                              date_beg = strftime(anytime(as.numeric(str_replace(str_extract(stable_text_split[, 2], ":(.*)"), ":", "")) - 86400 * input$cmv_bin_width), format = "%m/%d"),
                              status = str_replace(str_extract(stable_text_split[, 3], ":(.*)"), ":", ""),
                              percent = 100 * count / total_submissions) %>%
    mutate(label = sprintf("Submissions: %s (%.1f of Total%%)\n%s - %s",  count, percent, date_beg, date)) %>%
    select(label)
  
  time_series$x$data[[1]]$text <- change_text_label$label
  time_series$x$data[[2]]$text <- stable_text_label$label
  
  time_series <- time_series %>%
      layout(title = sprintf("\n%d submissions from %s - %s", 
                             nrow(reac_dat_cmv_sub()), strftime(input$cmv_time_range[1], format = "%m/%d/%Y"),
                                  strftime(input$cmv_time_range[2], format = "%m/%d/%Y")))
  time_series
})

```


Row {.tabset}
-------------------------------------------------------------------------------

### CMV Submission Content Wordcloud
```{r cmv_content_wc}
# Plot the wordcloud of the content of the filtered CMV data.
renderPlot({
  # Modified from day 17 notes
  reg <- "([^A-Za-z\\d#@']|'(?![A-Za-z\\d#@]))"   # custom regular expression to tokenize tweets
  
  # tokenize
  filtered_subs <- reac_dat_cmv_sub() %>%
    select(content) %>%
    filter(!str_detect(content, '^"')) %>%
    mutate(text = str_replace_all(content, "http[s]?://t.co/[A-Za-z\\d]+|&amp;", "")) %>%
    mutate(text = str_replace_all(text, "http[\\S]*", "")) %>%
    mutate(text = str_replace_all(text, "www.reddit.com", "")) %>%
    mutate(text = str_replace_all(text, "people", "")) %>%
    mutate(text = str_replace_all(text, "change", "")) %>%
    mutate(text = str_replace_all(text, "view", "")) %>%
    unnest_tokens(word, text, token = "words") %>%
    filter(!word %in% stop_words$word,
           str_detect(word, "[a-z]"))
  # plot
  filtered_subs %>%
    count(word) %>%
    with(wordcloud(word, n, max.words = 100))
                   
})
```

### CMV Submissions Table
```{r}
# Custom filtered data that doesn't include certain columns
# This is so the table will look better.
reac_table_cmv_sub <- reactive({
  reac_dat_cmv_sub() %>%
    select(OP_gave_delta, title, date) %>%
    mutate(date = paste(year(date), month(date), sep = "/"))
})

# Render the data table
renderDataTable(
  datatable(
  reac_table_cmv_sub(),
  options = list(DT.fillContainer = T,
                 autowidth = T, scrollY = 300,
                 autoheight = T,
                 pageLength = 30), 
  rownames = FALSE
      )
)
```


Search CMV Submissions by Title {data-orientation=rows}
==============================================================================

Search by Title {.sidebar}
--------------------------------------------------------

```{r read_model_dat}
# Read in another dataset.
dat_model <- read_feather("dat_model.feather")
indep_vars <- dat_model %>%
  select(-OP_gave_delta)

# For debugging purposes.
sumry_model_gave_delta <- dat_model %>% 
  group_by(OP_gave_delta) %>%
  summarise(count = n()) %>%
  mutate(prop = count / sum(count))
```

Search by specific keyword(s) to get an in-depth look at the properties of a specific r/changemyview post and its
author.

###

View wordclouds showing the author's most frequently used words in their prior submissions and the subreddits
they most frequently posted in.

###

Search the titles, submission dates, and subreddits of the author's prior submissions.

### Search by Title

```{r}
# Title selection
selectInput("cmv_title", "", sort(unique(dat_model$title)),
                selected = "CMV: Trump supports the Jewish people")

# Retrieve the specific title
reac_cmv_sub <- reactive({
 dat_cmv_subs %>%
    filter(title == input$cmv_title)
})
```


Row
--------------------------------------------

### Author
```{r}
# Show the name of the author prominently.
renderValueBox({
  valueBox(reac_cmv_sub()[["author"]],
         caption = "Author",
         color = "#0645AD"
  )
})
```


### Sentiment
```{r rend_senti}
# Customize the color depending on the sentiment value.
senti_col_ramp <- colorRamp(c("red", "white", "darkgreen"))
senti_colors <- function(num){
  colors <- senti_col_ramp(num)
  rgb(colors[1], colors[2], colors[3], maxColorValue = 255)
}

# Reactive CMV color based on current sentiment of selected title.
reac_senti_color <- reactive({
  senti_colors(reac_cmv_sub()[["sentiment"]])
})

# Display the sentiment value with the appropriate color.
renderValueBox({
  valueBox(round(reac_cmv_sub()[["sentiment"]], 1),
         caption = "Sentiment",
         color = reac_senti_color()
  )
})
```

### OP gave delta
```{r}
# Display whether or not the OP changed their opinion, red for no, green for yes.
# Also display statistics for how many comments are in the submission, how many direct comments
# there are, and how many OP replies.
renderValueBox(
  valueBox(
    ifelse(reac_cmv_sub()[["OP_gave_delta"]] == TRUE, "Opinion Changed",
           "No Opinion Change"),
    caption = sprintf("Posted: %s | %d User Comments | %d Direct Replies\n | %d Author Comments", 
                      strftime(reac_cmv_sub()[["date"]], format = "%m/%d   %H:%M %Z"),
                      reac_cmv_sub()[["num_user_comments"]], reac_cmv_sub()[["num_root_comments"]],
                      reac_cmv_sub()[["num_OP_comments"]]), 
    icon = "fa-id-card",
    color = ifelse(reac_cmv_sub()[["OP_gave_delta"]] == TRUE, "red", "green")
  )
)
```

Row
-------------------------------------------

### 
```{r}
# Retrieve the stats for the author of the currently selected title.
reac_auth_stats <- reactive({
  dat_model %>%
    filter(author == reac_cmv_sub()[["author"]], 
           created_utc == reac_cmv_sub()[["created_utc"]])
})


# Display how many submissions the author wrote prior to this changemyview 
# submission.
renderValueBox(
  valueBox(
    sprintf("%d", reac_auth_stats()[["num_prior_subs"]]),
    "Prior Submissions"
  )
)
```

### 
```{r}
# Display the average and total submission score of those previous submissions.
renderValueBox(
  valueBox(
    sprintf("%.2f (%.0f)", reac_auth_stats()[["avg_sub_score"]],
            reac_auth_stats()[["avg_sub_score"]] * reac_auth_stats()[["num_prior_subs"]]),
    "Average (Total) Submissions Score"
  )
)
```

### Submission Inequality
```{r}
# Custom color ramp for the gini index
col_ramp <- colorRamp(c("black", "white"))
gini_colors <- function(num){
  colors <- col_ramp(num)
  rgb(colors[1], colors[2], colors[3], maxColorValue = 255)
}

# The color for the current gini index
reac_gini_color <- reactive({
  gini_colors(reac_auth_stats()[["gini_index"]])
})

# Display the gini index as an "inequality" percentage and the appropriate color.
renderValueBox(
  valueBox(
    sprintf("% .1f%%", 100 * reac_auth_stats()[["gini_index"]]),
    color = reac_gini_color()
  )
)
```

Row {.tabset}
--------------------------------------------

### Submission Content

```{r}
# The content of the submission selected.
reac_cmv_sub_content <- reactive({
  writeLines(reac_cmv_sub()[["content"]])
})

# Display said content
renderPrint(reac_cmv_sub_content())
```

### Author Submission Content History Wordcloud
```{r}
# Select only the past history of the author in question.
reac_cmv_auth_past <- reactive({
  dat_cmv_auth_subs %>%
    filter(author == reac_cmv_sub()[["author"]]
           ) %>%
    select(-c(author, href, created_utc)) %>%
    mutate(date_new = paste(month(date), day(date), year(date), sep = "/"))
})

# Display a wordcloud of the content of the author's submission history.
renderPlot({
  # Modified from day 17 notes
  reg <- "([^A-Za-z\\d#@']|'(?![A-Za-z\\d#@]))"   # custom regular expression to tokenize tweets
  
  # tokenize
  past_subs <- reac_cmv_auth_past() %>%
    select(content) %>%
    filter(!str_detect(content, '^"')) %>%
    mutate(text = str_replace_all(content, "http[s]?://t.co/[A-Za-z\\d]+|&amp;", "")) %>%
    mutate(text = str_replace_all(text, "http[\\S]*", "")) %>%
    mutate(text = str_replace_all(text, "www.reddit.com", "")) %>%
    mutate(text = str_replace_all(text, "people", "")) %>%
    mutate(text = str_replace_all(text, "change", "")) %>%
    mutate(text = str_replace_all(text, "view", "")) %>% # Removing some commonly used words.
    unnest_tokens(word, text, token = "words") %>%
    filter(!word %in% stop_words$word,
           str_detect(word, "[a-z]"))
  # plot
  past_subs %>%
    count(word) %>%
    with(wordcloud(word, n, max.words = 100))
})
```

### Author Subreddit Participation History Wordcloud
```{r}
# Simple wordcloud showing what subreddits the given author participated in most.
renderPlot({
  # plot
  reac_cmv_auth_past() %>%
    count(subreddit) %>%
    with(wordcloud(subreddit, n, max.words = 50))
})
```

### Prior Submissions Table
```{r}
# Show a data table of the author's past submissions. Can also search it.
renderDataTable(
  datatable(
  reac_cmv_auth_past() %>% select(-date),
  options = list(DT.fillContainer = T,
                 autowidth = T, scrollY = 300,
                 autoheight = T,
                 pageLength = 30), 
  rownames = FALSE
      )
)
```

CMV Author Submissions {data-orientation=rows}
==============================================================================

Filter {.sidebar}
----------------------------------------------
```{r}
# Select a particular author.
selectizeInput("cmv_author", "", sort(unique(dat_cmv_subs$author)),
                selected = "oldie101")

# Select timeline type, a freqpoly of their submission activity or a timeline of
# their scores
radioButtons("timeline_type", "Timeline Type",
               c("Score" = "score",
                 "Submission Activity" = "sub_activity"),
               selected = "sub_activity")

# Select day smoothing parameter for the freqpoly
sliderInput(
  "past_bin_width",
  label = "Smoothing (Days - Submission Activity only)",
  min = 1,
  max = 365,
  value = 30
)
# selectizeInput("cmv_subreddit", "", unique(dat_cmv_auth_subs$subreddit))


```

###

View a timeline of the selected author's submission frequency with day smoothing.

### 
View a timeline of the author's submission scores.


Column
------------------------------------------------------

### Author

```{r}
# Display the name of the author prominently again.
renderValueBox({
  valueBox(input$cmv_author,
         caption = "Author",
         # href = reac_cmv_bauth_link(),
         color = "#0645AD"
  )
})
```

### CMV Submissions

```{r}
# Show how many changemyview submissions the author has written, with 
# a color matching the vertical lines in the timeline that indicate when they
# occurred.
renderValueBox({
  valueBox(length(reac_cmv_auth_cmvs()),
         caption = "Changemyview Submissions",
         color = "#00cc99"
  )
})
```

Row
-----------------------------------------------

###

```{r}
# Retrieve the past activity for the given author.
reac_cmv_auth_past_activity <- reactive({
  dat_cmv_auth_subs %>%
    filter(author == input$cmv_author
           ) %>%
    mutate(new_date = paste(year(date), month(date), sep = "/")) %>%
    select(-c(href, created_utc))
})

# Retrieve only the CMV submissions of the author
reac_cmv_auth_cmvs <- reactive({
  cmv_only <- reac_cmv_auth_past_activity() %>%
    filter(subreddit == "r/changemyview") %>%
    select(date)
  as.vector(cmv_only$date)
})

# Render the timeline desired
renderPlotly({
  if (input$timeline_type == "score"){
    plot <- (
      ggplot(reac_cmv_auth_past_activity(), 
                   aes(date, score)) +
      geom_line() + 
      labs(subtitle = "Dashed Red line(s) indicate CMV Submission(s)",
           y = "Score", 
           x = "Date"
           )
    )
    # Add in lines to indicate when their CMV submisisons took place
    for (cmv_sub in reac_cmv_auth_cmvs()){
      plot <- plot + geom_vline(aes(text = "CMV post"),
                                xintercept = cmv_sub, linetype = "dashed", color = "#00cc99", size = .3)
    }
    # A hackish way to make the tooltip better.
    time_series <- plotly_build(plot)
    raw_score_text <- time_series$x$data[[1]]$text
    score_text_split <- matrix(unlist(str_split(raw_score_text,
                                                     "<br />", 3)), ncol = 2, byrow = TRUE) 
    score_text_label <- tibble(date = strftime(anytime(as.numeric(str_replace(str_extract(score_text_split[, 1], ":(.*)"), ":", ""))), format = "%m/%d/%Y"),
                                score = str_replace(str_extract(score_text_split[, 1], ":(.*)"), ":", "")) %>%
      mutate(label = sprintf("Date: %s\nScore: %s", date, score)) %>%
      select(label)
  
    time_series$x$data[[1]]$text <- score_text_label$label
  
    time_series <- time_series %>%
      layout(title = sprintf("\nSubmission Scores | %d days smoothing", input$past_bin_width))
    
  } else {
    # Analagous things down here, with a different timeline type.
    plot <- ( 
      ggplot(reac_cmv_auth_past_activity(), 
                   aes(date)) +
      geom_freqpoly(binwidth = 86400 * input$past_bin_width, pad = FALSE) + 
      labs(subtitle = sprintf("Every %d days\nDashed Red line(s) indicate CMV Submission(s)", input$cmv_past_bin_width * 86400),
           x = "Date",
           y = "Submissions",
           color = "Opinion changed")
           )
    for (cmv_sub in reac_cmv_auth_cmvs()){
      plot <- plot + geom_vline(aes(text = "CMV post"),
                                xintercept = cmv_sub, linetype = "dashed", color = "#00cc99", size = .3)
    }
    
    time_series <- plotly_build(plot)
    
    raw_activity_text <- time_series$x$data[[1]]$text
    activity_text_split <- matrix(unlist(str_split(raw_activity_text,
                                                     "<br />", 3)), ncol = 2, byrow = TRUE) 
    activity_text_label <- tibble(count = str_replace(str_extract(activity_text_split[, 1], ":(.*)"), ":", ""),
                                  date = strftime(
                                    anytime(as.numeric(str_replace(
                                      str_extract(activity_text_split[, 1], ":(.*)"), ":", ""))), format = "%m/%d/%Y")) %>%
      mutate(label = sprintf("Submissions: %s\nDate: %s", count, date)) %>%
      select(label)
  
    time_series$x$data[[1]]$text <- activity_text_label$label
    
    time_series <- time_series %>%
      layout(title = sprintf("\nSubmission Activity | %d days smoothing", input$past_bin_width))
    }
  time_series
})
```


Row {.tabset}
------------------------------------------------------

### Submission Content Wordcloud
```{r  word_cloud}
# Render a wordcloud of the content of their past submissions.
renderPlot({
  # Modified from day 17 notes
  reg <- "([^A-Za-z\\d#@']|'(?![A-Za-z\\d#@]))"   # custom regular expression to tokenize tweets
  
  tst_auth_past <- reac_cmv_auth_past_activity() %>%
    filter(author == input$cmv_author)
  
  # tokenize
  past_subs <- tst_auth_past %>%
    filter(!str_detect(content, '^"')) %>%
    mutate(text = str_replace_all(content, "http[s]?://t.co/[A-Za-z\\d]+|&amp;", "")) %>%
    mutate(text = str_replace_all(text, "http[\\S]*", "")) %>%
    mutate(text = str_replace_all(text, "www.reddit.com", "")) %>%
    unnest_tokens(word, text, token = "words") %>%
    filter(!word %in% stop_words$word,
           str_detect(word, "[a-z]"))
  # plot
  past_subs %>%
    count(word) %>%
    with(wordcloud(word, n, max.words = 100))
                   
})
```

### Subreddit Participation Wordcloud
```{r subreddit_wordcloud}
# Render a wordcloud representing that author's most popular subreddits.
renderPlot({
  tst_auth_past <- reac_cmv_auth_past_activity() %>%
    filter(author == input$cmv_author)
  
  # plot
  tst_auth_past %>%
    count(subreddit) %>%
    with(wordcloud(subreddit, n, max.words = 100))
})
```

###  Past Submissions Table
```{r browse_past_subs}
# Render a table of that author's past submissions.
reac_table_past <- reactive({
  reac_cmv_auth_past_activity() %>%
    select(title, score, subreddit, date) %>%
    mutate(date = paste(month(date), day(date), year(date), sep = "/"))
})

renderDataTable(
  datatable(
  reac_cmv_auth_past_activity() %>% select(-date),
  options = list(DT.fillContainer = T,
                 autowidth = T, scrollY = 300,
                 autoheight = T,
                 pageLength = 30), 
  rownames = FALSE)
)
```